### 2015-05-08 cv-body.tex
Update CV

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2011--15]
Ph.D.\ Biology, Simon Fraser University, Burnaby, Canada\\ Variance and
extreme events in population ecology\\ Supervisors: Dr.\ Nicholas K.
Dulvy and Dr.\ Andrew B. Cooper\\ Canadian Fulbright Scholar to the
University of Washington in 2012--13
\item[2008--10]
M.Sc.\ Biology, Dalhousie University, Halifax, Canada\\ Trends, drivers,
and ecosystem effects of expanding global invertebrate fisheries\\
Supervisor: Dr.\ Heike K. Lotze.
(\href{http://seananderson.ca/papers/Anderson_MSc_2010.pdf}{PDF})\\
Canadian \href{http://goo.gl/nA1zE}{Governor General's Academic Gold
Medal} for the top-ranked Master's Natural Sciences and Engineering
thesis at Dalhousie University in 2010
\item[2004--07]
B.Sc.\ (Hons.) Environmental Science, Dalhousie University, Halifax,
Canada\\ Thesis title: How sustainable are emerging low-trophic level
fisheries on the Scotian Shelf? Supervisors: Dr.\ Heike K. Lotze and
Dr.\ Ransom A. Myers.
(\href{http://seananderson.ca/papers/Anderson_HSc_2006.pdf}{PDF})\\
First Class Honours \& Environmental Programmes Honour Society Medal
\item[2001--03]
B.Sc.\ Candidate (Hons.) Kinesiology, University of Waterloo, Waterloo,
Canada Transferred to Dalhousie University in 2004.
\end{description}

@@

@@

the modern oceans. In press. (\emph{*Authors contributed equally}).

@@

of Animal Ecology. In press.

@@

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2015]
Trebilco, R., N.K. Dulvy, \textbf{S.C. Anderson}, A.K. Salomon. The
paradox of inverted biomass pyramids in kelp forest fish communities. In
review.
\end{description}

>>>>

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2011--15]
Ph.D.\ Biology, Simon Fraser University, Burnaby, Canada\\ Variance and
extreme events in population ecology\\ Fulbright Scholar to the
University of Washington in 2012--13\\ Dean of Graduate Studies
Convocation Medal
\item[2008--10]
M.Sc.\ Biology, Dalhousie University, Halifax, Canada\\ Trends, drivers,
and ecosystem effects of expanding global invertebrate fisheries\\
Canadian \href{http://goo.gl/nA1zE}{Governor General's Academic Gold
Medal}
\item[2004--07]
B.Sc.\ (Hons.) Environmental Science, Dalhousie University, Halifax,
Canada\\ First Class Honours \& Environmental Programmes Honour Society
Medal
\item[2001--03]
B.Sc.\ Candidate (Hons.) Kinesiology, University of Waterloo, Waterloo,
Canada; transferred to Dalhousie University in 2004.
\end{description}

@@

the modern oceans. Science. 348(6234): 567--570.
\url{http://doi.org/10.1126/science.aaa6635} (\emph{*Authors contributed
equally}).

@@

@@

of Animal Ecology. 83(3):840--850.

@@

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2015]
Monnahan, C.C., K. Ono, S.C Anderson, M.B. Rudd, A.C. Hicks, F.
Hurtado-Ferro, K.F. Johnson, P.T. Kuriyama, R.R. Licandeo, C.C. Stawitz,
I.G. Taylor, J.L. Valero. The effect of length bin structures on growth
estimation in integrated age-structured stock assessments. Submitted.
\item[2015]
Kuriyamaa, P.T., F. Hurtado-Ferro, K. Ono, A.C. Hicks, I.G. Taylor, R.R.
Licandeo, K.F. Johnson, S.C. Anderson, C.C. Monnahan, M.B. Rudd, C.C.
Stawitz, J.L. Valero. An empirical weight-at-age approach reduces
estimation bias compared to modeling parametric growth in integrated,
statistical stock assessment models when growth is time varying.
Submitted.
\item[2015]
Trebilco, R., N.K. Dulvy, \textbf{S.C. Anderson}, A.K. Salomon. The
paradox of inverted biomass pyramids in kelp forest fish communities. In
revision.
\end{description}
